EEOB563 -- Assignment #3

### 2019-02-21 assignments/3/assignment_3.Rmd
Started Assignment 3 Part II

/----------------------------------------------------------------------------------------------------------------------------------------- Dolphin
|
|                                                          /--------------------------------------- Hippopotamus
|                                                          |
|                                                          |                                      /--------------------------------------- Cow
|                   /-------------------------------------13                                      |
|                   |                                      +-------------------------------------11--------------------------------------- Giraffe
|                   |                                      |                                      |
|                   |                                     12                                      \--------------------------------------- Goat
|                   |                                      |
|                   |                                      \--------------------------------------- Sheep
|                   |
\------------------14 Camel
                    |
                    + Sperm whale
                    |
                    + Blue whale
                    |
                    \ Pig
```
Please look at my paup log file for additional info, here is also the FASTA file I wrote and the Nexus file I generated from it.

>>>>

/----------------------------------------------------------------------------------------------------------------------------------------- Dolphin
|
|                                                          /--------------------------------------- Hippopotamus
|                                                          |
|                                                          |                                      /--------------------------------------- Cow
|                   /-------------------------------------13                                      |
|                   |                                      +-------------------------------------11--------------------------------------- Giraffe
|                   |                                      |                                      |
|                   |                                     12                                      \--------------------------------------- Goat
|                   |                                      |
|                   |                                      \--------------------------------------- Sheep
|                   |
\------------------14 Camel
                    |
                    + Sperm whale
                    |
                    + Blue whale
                    |
                    \ Pig
```
Please look at my [paup log](https://github.com/Thyra/EEOB563/blob/master/assignments/3/3c.log) file for additional info, here is also the [FASTA file](https://github.com/Thyra/EEOB563/blob/master/assignments/3/3.fa) I wrote and the [Nexus file](https://github.com/Thyra/EEOB563/blob/master/assignments/3/3.nxs) I generated from it.

# Part II
I aligned the sequences with Pal2Nal (vertebrate table, output format FASTA, I told it to remove gaps, otherwise elephant and human were shorter than the others. Otherwise I left the standard options), I got a lot of warnings that I does not correspond to ATA but it seems like it worked ([result file](https://github.com/Thyra/EEOB563/blob/master/assignments/3/cob_aligned.fa)). I converted it into a [Nexus file](https://github.com/Thyra/EEOB563/blob/master/assignments/3/cob_aligned.nxs).

## 4
Please look at the complete log file of the analysis [here](https://github.com/Thyra/EEOB563/blob/master/assignments/3/4.log). All the trees that were found had a very similar score and only marginally different topologie, the run with 100 reps was the most different from the rest. It reminds me of the trees I did by hand where I also found the best tree very early. So either this is just the global optimum and very easy to find or it is a local optimum and none of the methods were thorough enough to find the global optimum.

## 5
